Portable Development Methodology

### 2024-02-05 latex/ms.tex
.

\section{Introduction}
Widespread software development practices like agile~\cite{abrahamsson2017agile} are not concrete enough thus multiple versions of each of them exist in software development.
Loosely defined practices introduce non-portability issues through time and space, increasing development costs.

@@

\section{Make}
Make~\cite{fowler1990case} has been used since 1970s and some of its basic features were standardized by POSIX\@.
Moreover the Makefile can be combined with any version control system, container registry provider and text editor thus preventing `app/vendor lock-in' situations.

Use cases of the Makefile include:
\begin{itemize}
	\item regression testing and debugging, to ensure that changes to \texttt{code} do not alter the generated data,
	\item portable development environment across multiple \texttt{developers},
	\item portable development environment across time.
\end{itemize}

\section{Containers}
Containers were standardized with the Open Container Initiative\footnote{\url{https://opencontainers.org/}} and there exist alternatives such as Podman that could be used as drop-in replacements for Docker.

>>>>

\section{Introduction}
Widespread software development practices like agile~\cite{abrahamsson2017agile} are not concrete enough, thus multiple versions of each of them exist in software development.
Loosely defined practices introduce non-portability issues through time and space, increasing development costs.

@@

\section{Requirements}
POSIX utilities and shell are the base of any Unix system today.
However, by itself is not enough to cover most of the modern needs of software development, namely: machine learning and web applications.

Containers combined with POSIX utilities and shell can be used to create isolated environments.
Containers were standardized with the Open Container Initiative\footnote{\url{https://opencontainers.org/}} and there exist alternatives such as Podman that could be used as drop-in replacements for Docker.
